---
title: "Data Products"
author: "Marguerite Smith"
date: "30 March 2017"
output: html_document
runtime: shiny
---

```{r setup, echo=FALSE}
knitr::opts_knit$set(progress = TRUE, verbose = TRUE)
knitr::opts_chunk$set(echo = FALSE)
```

```{r fullcode, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
require(twitteR)
require(data.table)
require(leaflet)
require(ggmap)
require(httr)

########  Setting up the Twitter search call

# Declare Twitter API Credentials
appname <- "map_puppers"
api_key <- "gRzJTRnB4XqFWQfMVa9YroTqx"
api_secret <- "OynCqPjaaDL1sq6BPzpyTeLpzB2xGJtvdx7GgYW9y103nnYWT9"
token <- "16111017-NN8C0KYMwZIhdjdyENncEd04E3UNVi3gMlDM5zRWi" # From dev.twitter.com
token_secret <- "CH9KQceKPcULfw8iWcxVNSvptCGfGnaNo6nHLy2LxBEzU" # From dev.twitter.com

# Create Twitter Connection
setup_twitter_oauth(api_key, api_secret, token, token_secret)


getTweets <- function(numTweets) {
      print(paste("Getting up to",numTweets,"images."))
      tweets_raw <- userTimeline('dogwatisaw', n = numTweets*2,
                                 includeRts = FALSE, excludeReplies = TRUE)
      tweets.df <- twListToDF(tweets_raw)
      drawings <- tweets.df[grep(" https://t.co/",tweets.df$text),]
      if(nrow(drawings) > numTweets) {
            drawings <- drawings[1:numTweets,]
      }
      print(paste("Results count:",nrow(drawings)))
      print(drawings$text)
      return(drawings)
}



mapTweets <- function(drawings) {
      ###### Start by processing the tweets

      drawings$description <- gsub("(^.*)( -.*$)", "\\1", x=drawings$text)
      # print(drawings$description)
      drawings$image <- paste("https://", 
                              gsub("(^.*https://)(.*$)", 
                              "\\2", x=drawings$text), 
                              sep="")
      drawings$location <- gsub(
        "(.* - )([[:digit:]]+:?[[:digit:]]*[[AaPp]m]? ?)?(.*)( https:.*$)",
        "\\3",x=drawings$text)
      
      # Many thanks to https://regex101.com/ for making it easier to sort that out!
      print(drawings$location)
      
      embeds <- data.frame("body" = character())
      
      for(id in drawings$id) {
            twiturl <- paste("https://publish.twitter.com/oembed?url=https%3A%2f%2ftwitter.com%2fdogwatisaw%2fstatus%2f",id,sep="")
            newurl <- as.character(content(GET(twiturl))$html)
            embeds <- rbind(embeds, data.frame(body = newurl))
      }
      
      # The URL for the script is actually incorrect - try adding in https://
      # Original: <script async src="//platform.twitter.com/widgets.js" charset="utf-8"></script>
      # Want: <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
      
      #embeds$body <- gsub('src="//platform', 'src="https://platform', embeds$body)

      ######## Making the lat/long table

      puppers_latlong <- data.frame("lat" = numeric(), "lng" = numeric())
      for(loc in drawings$location) {
        loc <- paste0(loc, ", Gothenburg, Sweden")
        geo_reply = geocode(loc, output='all', messaging=TRUE, override_limit=TRUE)
      
          this_lat <- geo_reply$results[[1]]$geometry$location$lat
          this_lng <- geo_reply$results[[1]]$geometry$location$lng
      
        new_coords <- data.frame( "lat" = this_lat, "lng" = this_lng)
        puppers_latlong <- rbind(puppers_latlong, new_coords)
      }
      
      
      ######## Making our markers
      
      puppers_popups <- embeds$body
      #print(puppers_popups)
      
      map <- 
            puppers_latlong %>%
            leaflet() %>%
            setView(lat = 57.6987865, lng = 11.9745282, zoom=12) %>%
            addTiles() %>%
            addMarkers(popup = puppers_popups, 
                       clusterOptions = markerClusterOptions())
      return(map)
}
```

## Map_puppers
### 30 March 2017

The Twitter feed [@dogwatisaw](https://www.twitter.com/dogwatisaw) is a fun feed where the poster notices dogs around town, draws them from memory later, and then posts the pictures along with a short description.

This is a very basic webpage that does the following through R:

* Reads up to the last 20 tweets from the Twitter user @dogwatisaw, excluding replies and retweets
* Retains only the tweets containing pictures, as defined by having an https://t.co/ link in them
* Parses the body of the text to get the following:
    + The location
    + The t.co link
    + The tweet ID
* Uses the tweet ID and Twitter's Publish API to get the embeddable code
* Uses the text location and Google's geolocate to get an approximate latitude and longitude
* Uses leaflet() to plot the sightings and puts the embedded tweet in the popup

## The pupper map


```{r echo=FALSE}
shinyApp(
      ui = fluidPage(
            titlePanel("Dogs in Gothenburg"),
            sidebarLayout(
                  sidebarPanel(
                        selectInput("numTweets", 
                                 label="How many tweets to display?", 1:20
                                 #, selected=17),
                        ),
                        submitButton("Map the pups!"),
                        textOutput("numOutput")
                        ),
                  mainPanel(leafletOutput('puppers', height = 350))
            )
      ),
      server = function(input, output) {
            output$puppers <- renderLeaflet(
                  mapTweets(
                        getTweets(as.numeric(input$numTweets))
                  )
            )
      }

)
```